---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "",
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

# **Status and Trends of Caribbean Coral Reefs: 1980-2023**


## 1. Introduction

## 2. Code

### Functions

* `data_descriptors.R` Get number of sites, surveys, datasets, first and last year of monitoring.
* `graphical_par.R` Graphical parameters, including colors and fonts.
* `theme_graph.R` Main ggplot theme for the plots of the reports.
* `theme_map.R` Main ggplot theme for the maps of the reports.

### Cleaning and selection (`a_`)



### Extract indicators (except benthic cover) (`b_`)


### Models (benthic cover) (`c_`)



### Figures and tables (`d_`)



## 3. Reproducibility parameters

```{r echo=FALSE, message=FALSE}

# 1. Print session info ----

devtools::session_info(c("sf", "terra", "tidyverse", "tidymodels"))

```
