---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "",
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

# **Status and Trends of Caribbean Coral Reefs: 1970-2024**


## 1. Introduction

## 2. Code

### Functions

* `data_descriptors.R` Get number of sites, surveys, datasets, first and last year of monitoring.
* `graphical_par.R` Graphical parameters, including colors and fonts.
* `plot_region.R` Regional background map.
* `theme_graph.R` Main ggplot theme for the plots of the reports.
* `theme_map.R` Main ggplot theme for the maps of the reports.

### Cleaning and selection (`a_`)

* `a01_select_benthic-data.R`
* `a02_benthic-data_sources.R`
* `a03_clean_shp.R`
* `a07_reef-buffer.js`
* `a08_clean_cyclones.R`
* `a09_extract_sst-anom-year.R`

### Extract indicators (`b_`)

* `b05_extract_indicator_cyclones`

### Models (benthic cover) (`c_`)

* `c01_explo_benthic-data.R` Exploratory analyses of benthic cover data.

### Models (fish biomass) (`d_`)


### Figures and tables (`e_`)

* `e02_region_map.R`
* `e03_territories_map.R`
* `e04_region_sst.R`
* `e05_territories_sst.R`
* `e06_region_cyclones.R` 
* `e07_territories_cyclones.R` 
* `e08_region_spatio-temporal.R`
* `e09_territories_spatio-temporal.R`
* `e11_other-indicators.R`

## 3. Reproducibility parameters

```{r echo=FALSE, message=FALSE}

# 1. Print session info ----

devtools::session_info(c("sf", "terra", "tidyverse", "tidymodels"))

```
