---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "",
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

# **Status and Trends of Caribbean Coral Reefs: 1980-2024**


## 1. Introduction

## 2. Code

### Functions

* `combine_model_data.R` Combine benthic cover model results.
* `combine_plot_trends.R` Combine temporal trend plots produced by the function _plot_trends.R_.
* `create_chapter_doc.qmd` Countries and territories chapter template.
* `data_descriptors.R` Get number of sites, surveys, datasets, first and last year of monitoring.
* `download_predictors.R` Download predictors extracted through GEE and stored on Google Drive.
* `extract_coeff.R` Extract linear models _a_ and _b_ coefficients.
* `extract_mankendall.R` Calculate temporal trends using Man Kendall test.
* `graphical_par.R` Graphical parameters, including colors and fonts.
* `plot_pred_obs.R` Plot predicted _vs_ observed values (model evaluation).
* `plot_region.R` Regional background map.
* `plot_residuals.R` Plot residuals (model evaluation).
* `plot_trends.R` Plot temporal trends.
* `plot_vimp.R` Plot Variable Importance Plot (VIMP).
* `prepare_benthic_data.R` Prepare benthic cover data.
* `plot_pdp.R` Plot Partial Dependence Plot (PDP).
* `plot_prediction_map.R` Plot the map of the Caribbean with predicted values.
* `render_qmd.R` Render script _create_chapter_doc.qmd_.
* `theme_graph.R` Main ggplot theme for plots.
* `theme_map.R` Main ggplot theme for maps.
* `theme_map_area.R` ggplot theme for countries and territories maps.

### Cleaning and selection (`a_`)

* `a01_select_topo-bathy.js` Extract topography and bathymetry using [Google Earth Engine](https://earthengine.google.com/) (GEE).
* `a02_clean_shp.R` Clean shapefiles from different sources.
* `a03_select_benthic-data.R` Extract benthic cover data from [gcrmndb_benthos](https://github.com/GCRMN/gcrmndb_benthos).
* `a04_benthic-data_sources.R` Extract lists of datasetID and contributors details.
* `a05_reef-buffer.js` Create coral reef buffer polygons at 20, 50, and 100 km using [GEE](https://earthengine.google.com/).
* `a06_reef-buffer-area.R` Join reef buffer with areas' boundaries.
* `a07_clean_cyclones.R` Clean cyclones data.
* `a08_download_crw-year.R` Extract netCDF file aggregated per year from Coral Reef Watch (CRW).

### Indicators' extraction (`b_`)

* `b03_extract_indicator_population.js` Extract population indicators using [GEE](https://earthengine.google.com/).
* `b04_extract_indicator_sst.R` Extract SST indicators.
* `b05_extract_indicator_cyclones.R` Extract cyclones indicators.

### Models (benthic cover) (`c_`)

* `c01_explo_benthic-data.R` Exploratory analyses of benthic cover data.
* `c07_extract_predictor_crw.R` Extract DHW max, SSTa max, and SSTa mean.
* `c09_model_tuning_rf.R` Perform hyper parameters tuning for Random Forest models.
* `c09_model_tuning_xgb.R` Perform hyper parameters tuning for XGBoost models.
* `c10_model_bootstrap_rf.R` Run bootstrap predictions using Random Forest models.
* `c10_model_bootstrap_xgb.R` Run bootstrap predictions using XGBoost models.

### Models (fish biomass) (`d_`)


### Figures and tables (`e_`)

* `e01_materials-and-methods.R` Produce figures for the Materials and Methods.
* `e02_region_map.R` Produce map of the region.
* `e03_areas_map.R` Produce contextual maps for areas.
* `e04_region_sst.R` Produce figures for SST for the region.
* `e05_areas_sst.R` Produce figures for SST for areas.
* `e06_region_cyclones.R` Produce figures for cyclones for the region.
* `e07_areas_cyclones.R` Produce figures for cyclones for areas.
* `e08_region_spatio-temporal.R` Produce figures for spatio-temporal distribution of monitoring for the region.
* `e09_areas_spatio-temporal.R` Produce figures for spatio-temporal distribution of monitoring for areas.
* `e10_benthic-cover_trends.R` Produce figures for benthic cover temporal trends.
* `e11_other-indicators.R` Produce figures, tables, and numbers for other indicators.

### Writing and sharing (`f_`)

* `f01_create-chapters.R` Generate .docx chapters for areas.
* `f02_authors-contribution.R` Export author's contributions .xlsx file. 

## 3. Reproducibility parameters

```{r echo=FALSE, message=FALSE}

# 1. Print session info ----

devtools::session_info(c("sf", "terra", "tidyverse", "tidymodels"))

```
