---
title: "Chapter `r nb_chapter`"
subtitle: "`r str_to_title(territory_name)`"
output:
  word_document:
    reference_docx: styles.docx
editor: source
---

```{r echo=FALSE, message=FALSE}

require(tidyverse)
require(readxl)
require(flextable)

```

\
<div custom-style="textb">

```{r echo=FALSE, message=FALSE}

list_authors <- read_xlsx("../../figs/06_additional/05_contributors/contributors_area.xlsx") %>% 
  filter(area == area_i) %>% 
  mutate(name = str_replace_all(name, "\\*", "\\\\*")) %>% 
  select(name) %>% 
  pull()

```

**Authors:** `r list_authors`.

\

\*AGRRA data contributor(s).

\

</div>

<div custom-style="explanations">
The list of authors has been generated automatically in alphabetical order. It can be rearranged to reflect the relative importance of each contribution, with the main authors appearing at the beginning of the list.
</div>

\newpage

## Introduction

<div custom-style="explanations">
**[Maximum number of words of the section: 170]**
</div>

<div custom-style="text">

```{r echo=FALSE, message=FALSE}

data_intro <- read_xlsx("../../figs/01_part-1/tbl-1.xlsx") %>% 
  filter(area == area_i)

```

`r area_i` hosts `r pull(data_intro[1,"reef_area_abs"])` km^2^ of coral reefs, which represent `r pull(data_intro[1,"reef_area_rel_caribbean"])`% of the Caribbean’s total coral reef extent.

<div custom-style="todo">
A paragraph about the country or territory
</div>

</div>

\newpage

## Threats

### Thermal regime

<div custom-style="explanations">
**[Maximum number of words of the section: 130]**
</div>

<div custom-style="text">

```{r echo=FALSE, message=FALSE}

sst_lt <- read_xlsx("../../figs/01_part-1/tbl-3.xlsx") %>% 
  filter(area == area_i) %>% 
  select(mean_sst) %>% 
  pull()

sst_trend <- read_xlsx("../../figs/01_part-1/tbl-3.xlsx") %>% 
  filter(area == area_i) %>% 
  select(sst_increase) %>% 
  pull()

sst_rate <- read_xlsx("../../figs/01_part-1/tbl-3.xlsx") %>% 
  filter(area == area_i) %>% 
  select(warming_rate) %>% 
  pull()

```

The long-term average in SST from 1985 to 2024 over coral reefs of `r area_i` was `r sst_lt` °C. Over this period, SST increased by `r sst_trend` °C, representing a warming rate of `r sst_rate` °C per year (**Figure 2.`r nb_chapter`.1**).

<div custom-style="todo">
A paragraph about the impacts of bleaching events (1998, 2005, and 2023-2024)
</div>

```{r echo=FALSE, message=FALSE}

figure_path <- paste0("../../figs/02_part-2/fig-2/", territory_name, ".png")

```

![](`r figure_path`)

**Figure 2.`r nb_chapter`.1.** Average Sea Surface Temperature (SST) anomaly from July 1985 to July 2024 over coral reefs of `r area_i`. The black line is the long-term trend in SST anomaly, values below this line are negative SST anomalies (*i.e.* cooler than long-term trend), and values above this line are positive SST anomalies (*i.e.* warmer than long-term trend).

</div>

\newpage

### Hurricanes

<div custom-style="explanations">
**[Maximum number of words of the section: 100]**
</div>

```{r echo=FALSE, message=FALSE}

data_cyclones_i <- data_cyclones %>% 
  filter(area == area_i)

nb_storm <- length(unique(data_cyclones_i$ts_id))

data_cyclones_i <- data_cyclones_i %>% 
  filter(area == area_i) %>% 
  filter(windspeed >= 100)

nb_cyclone <- length(unique(data_cyclones_i$ts_id))

data_cyclones_i <- data_cyclones_i %>% 
  filter(area == area_i) %>% 
  filter(windspeed == max(windspeed))

name_cyclone <- str_to_title(data_cyclones_i$ts_name)

year_cyclone <- year(data_cyclones_i$time)

dist_cyclone <- round(data_cyclones_i$dist)

speed_cyclone <- round(data_cyclones_i$windspeed)

```

<div custom-style="text">

Between 1980 and 2024, a total of `r nb_storm` tropical storms passed within 100 km distance from a coral reef of `r area_i`, and of these `r nb_cyclone` were characterized by sustained wind speed greater than 100 km.h^-1^ (**Figure 2.`r nb_chapter`.2**). The hurricane with the highest sustained wind speed over the studied period was the hurricane `r name_cyclone`, in `r year_cyclone`, which passed `r dist_cyclone` km from a coral reef with sustained wind speed of `r speed_cyclone` km.h^-1^.

\

```{r echo=FALSE, message=FALSE}

figure_path <- paste0("../../figs/02_part-2/fig-3/", territory_name, ".png")

```

![](`r figure_path`)

**Figure 2.`r nb_chapter`.2.** Maximum sustained wind speed of tropical storms passing within 100 km of a coral reef between 1980 and 2024 in `r area_i`. Colors correspond to the cyclone’s Saffir-Simpson category along its entire track. However, the values of sustained wind speed are extracted from the nearest tropical storm position from a coral reef. For this reason, some sustained wind speed values are below the lower threshold of category 1 Saffir-Simpson scale (*i.e.* 119 km.h^-1^). Note that cyclones passing more than 100 km away from coral reefs of `r area_i` are not represented, although they can have had an impact.

</div>

\newpage

### Other threats

<div custom-style="explanations">
**[Maximum number of words of the section: 200]**
</div>

<div custom-style="todo">
You can replace the subsection "Other threats" by any major threats impacting coral reefs of `r area_i`
</div>

\newpage

## Trends in benthic cover

<div custom-style="explanations">
**[Maximum number of words of the section: 400]**
</div>

<div custom-style="text">

```{r echo=FALSE, message=FALSE}

data_monitoring <- read_xlsx("../../figs/01_part-1/tbl-4.xlsx") %>% 
  filter(area == area_i) %>% 
  select(nb_sites, nb_surveys, nb_datasets, first_year, last_year) %>% 
  mutate(across(c(nb_sites, nb_surveys), ~format(.x, big.mark = ",")))

```

Temporal trends in the percentage cover of benthic categories from 1980 to 2024 were estimated using data from `r pull(data_monitoring[1, "nb_datasets"])` datasets (**Figure 2.`r nb_chapter`.3**) encompassing `r pull(data_monitoring[1, "nb_sites"])` monitoring sites. These data were collected through `r pull(data_monitoring[1, "nb_surveys"])` surveys conducted between `r pull(data_monitoring[1, "first_year"])` and `r pull(data_monitoring[1, "last_year"])`.

\

```{r echo=FALSE, message=FALSE}

figure_path <- paste0("../../figs/02_part-2/fig-4/", territory_name, ".png")

```

![](`r figure_path`)

**Figure 2.`r nb_chapter`.3.** Temporal distribution of surveys from datasets included in the analyses to model temporal trends of the three benthic categories.

\newpage

```{r echo=FALSE, message=FALSE}

figure_path <- paste0("../../figs/02_part-2/fig-1/", territory_name, ".png")

```

![](`r figure_path`)

**Figure 2.`r nb_chapter`.4.** Spatio-temporal distribution of benthic cover monitoring sites across `r area_i`. Sites that were monitored for the longest period of time are represented on top of the sites monitored for fewer years.

</div>

\newpage

<div custom-style="todo">
A paragraph describing the temporal trends, major events that can explain the patterns, and any references to compare the trends with
</div>

\

```{r echo=FALSE, message=FALSE}

figure_path <- paste0("../../figs/02_part-2/fig-5/", territory_name, ".png")

```

![](`r figure_path`){width=100%}

<div custom-style="text">

**Figure 2.`r nb_chapter`.5.** Modeled temporal trends of benthic percentage cover for hard coral (A), algae (B), and other fauna (C) in `r area_i` from 1980 to 2024. The bold lines indicate the modeled mean cover, while the shaded ribbon represents the 95% confidence intervals. Points denote the annual mean of observed data, and the line ranges depict the corresponding standard deviations.

</div>

\newpage

## References

<div custom-style="explanations">
**[Maximum number of references: 15]**

In the text, the format of the citation should be (Alvarez-Filip et al., 2009) or Alvarez-Filip et al. (2009).

In this section, the citation should follow the APA style:

Alvarez-Filip, L., Dulvy, N. K., Gill, J. A., Côté, I. M., & Watkinson, A. R. (2009). Flattening of Caribbean coral reefs: region-wide declines in architectural complexity. Proceedings of the Royal Society B: Biological Sciences, 276(1669), 3019-3025.

</div>
