---
title: "`r area_i`"
format:
  docx:
    fig-align: "center"
editor: source
---

```{r echo=FALSE, message=FALSE}

require(tidyverse)
require(readxl)
require(flextable)

```

\
\

## 1. Introduction

\

```{r echo=FALSE, message=FALSE}

figure_path <- paste0("../../figs/02_part-2/fig-0/", territory_name, ".png")

```

![](`r figure_path`){width=30%}

\

```{r echo=FALSE, message=FALSE}

read_xlsx("../../figs/01_part-1/tbl-1.xlsx") %>% 
  filter(area == area_i) %>% 
  select(reef_area_abs, reef_area_rel) %>% 
  t() %>% 
  as.data.frame() %>% 
  bind_cols(V2 =  c("Coral reef extent (km^2)", "Coral reef extent relative to the Caribbean"), .) %>% 
  flextable() %>% 
  delete_part(part = "header") %>% 
  theme_box() %>% 
  set_table_properties(., width = 0.95, layout = "autofit")

```

\newpage

```{r echo=FALSE, message=FALSE}

figure_path <- paste0("../../figs/02_part-2/fig-1/", territory_name, ".png")

```

![](`r figure_path`)

**Figure 2.`r nb_chapter`.1** Spatio-temporal distribution of benthic cover monitoring sites across `r area_i`. Sites that were monitored for the longest period of time are represented on top of the sites monitored for fewer years.

\newpage

## 2. Major threats

### 2.1 Thermal regime

\

```{r echo=FALSE, message=FALSE}

figure_path <- paste0("../../figs/02_part-2/fig-2/", territory_name, ".png")

```

![](`r figure_path`)

**Figure 2.`r nb_chapter`.2.** Average Sea Surface Temperature (SST) anomaly from 1985 to 2024 over coral reefs of `r area_i`. The black line is the long-term trend in SST anomaly, values below this line are negative SST anomalies (*i.e.* cooler than long-term trend), and values above this line are positive SST anomalies (*i.e.* warmer than long-term trend).

\

```{r echo=FALSE, message=FALSE}

sst_lt <- read_xlsx("../../figs/01_part-1/tbl-3.xlsx") %>% 
  filter(territory == area_i) %>% 
  select(mean_sst) %>% 
  pull()

sst_trend <- read_xlsx("../../figs/01_part-1/tbl-3.xlsx") %>% 
  filter(territory == area_i) %>% 
  select(sst_increase) %>% 
  pull()

sst_rate <- read_xlsx("../../figs/01_part-1/tbl-3.xlsx") %>% 
  filter(territory == area_i) %>% 
  select(warming_rate) %>% 
  pull()

```

The long-term average in SST from 1985 to 2024 over coral reefs of `r area_i` was `r sst_lt` °C. Over this period, SST increased by `r sst_trend` °C, representing a warming rate of `r sst_rate` °C per year

\

\newpage

### 2.2 Hurricanes

\

```{r echo=FALSE, message=FALSE}

figure_path <- paste0("../../figs/02_part-2/fig-3/", territory_name, ".png")

```

![](`r figure_path`)

**Figure 2.`r nb_chapter`.3.** Maximum sustained wind speed of tropical storms passing within 100 km of a coral reef between 1980 and 2023 in `r area_i`. Colors correspond to the cyclone’s Saffir-Simpson category along its entire track. However, the values of sustained wind speed are extracted from the nearest tropical storm position from a coral reef. For this reason, some sustained wind speed values are below the lower threshold of category 1 Saffir-Simpson scale (*i.e.* 119 km.h^-1^). Note that cyclones passing more than 100 km away from coral reefs of `r area_i` are not represented, although they can have had an impact.

\newpage

### 2.3 Other threats

\

\newpage

## 3. Trends in benthic cover

\

**Table 2.`r nb_chapter`.2.** Summary of monitoring data used to model temporal trends of major benthic categories.

```{r echo=FALSE, message=FALSE}

read_xlsx("../../figs/01_part-1/tbl-4.xlsx") %>% 
  filter(area == area_i) %>% 
  select(nb_sites, nb_surveys, nb_datasets, first_year, last_year) %>% 
  t() %>% 
  as.data.frame() %>% 
  bind_cols(V2 =  c("Number of sites", "Number of surveys", "Number of datasets",
                    "First year with data", "Last year with data"), .) %>% 
  flextable() %>% 
  delete_part(part = "header") %>% 
  theme_box() %>% 
  set_table_properties(., width = 0.95, layout = "autofit")

```

\

```{r echo=FALSE, message=FALSE}

figure_path <- paste0("../../figs/02_part-2/fig-4/", territory_name, ".png")

```

![](`r figure_path`)

**Figure 2.`r nb_chapter`.4.** Temporal distribution of surveys from datasets included in the analyses to model temporal trends of major benthic categories.

\newpage

## References

\

TO BE ADDED
