---
title: "`r area_i`"
format:
  docx:
    fig-align: "center"
editor: source
---

```{r echo=FALSE, message=FALSE}

require(tidyverse)
require(readxl)
require(flextable)

```

\
\

```{r echo=FALSE, message=FALSE}

list_authors <- read_xlsx("../../figs/05_supp-mat/tbl-4.xlsx") %>% 
  filter(area == area_i) %>% 
  select(name) %>% 
  pull()

```

**Authors:** `r list_authors`

\

## 1. Introduction

\

```{r echo=FALSE, message=FALSE}

figure_path <- paste0("../../figs/02_part-2/fig-0/", territory_name, ".png")

```

![](`r figure_path`){width=30%}

\

```{r echo=FALSE, message=FALSE}

read_xlsx("../../figs/01_part-1/tbl-1.xlsx") %>% 
  left_join(., read_xlsx("../../figs/01_part-1/tbl-2.xlsx")) %>% 
  filter(area == area_i) %>% 
  select(reef_area_abs, reef_area_rel, pop_reef_2020, pop_percent, pop_reef_change) %>% 
  mutate(across(c("reef_area_rel", "pop_percent", "pop_reef_change"), ~paste0(.x, " %")),
         reef_area_abs = paste0(reef_area_abs, " km²")) %>% 
  t() %>% 
  as.data.frame() %>% 
  bind_cols(V2 =  c("Coral reef extent",
                    "Coral reef extent relative to the Caribbean",
                    "Number of inhabitants living within 20 km from a reef (in 2020)",
                    "Number of inhabitants living within 20 km from a reef relative to the total number of inhabitants (in 2020)",
                    "Change in the number of inhabitants living within 20 km from a reef between 2000 and 2020"), .) %>% 
  flextable() %>% 
  delete_part(part = "header") %>% 
  theme_box() %>% 
  set_table_properties(., width = 0.95, layout = "autofit")

```

\newpage

```{r echo=FALSE, message=FALSE}

figure_path <- paste0("../../figs/02_part-2/fig-1/", territory_name, ".png")

```

![](`r figure_path`)

**Figure 2.`r nb_chapter`.1** Spatio-temporal distribution of benthic cover monitoring sites across `r area_i`. Sites that were monitored for the longest period of time are represented on top of the sites monitored for fewer years.

\newpage

## 2. Major threats

### 2.1 Thermal regime

\

```{r echo=FALSE, message=FALSE}

figure_path <- paste0("../../figs/02_part-2/fig-2/", territory_name, ".png")

```

![](`r figure_path`)

**Figure 2.`r nb_chapter`.2.** Average Sea Surface Temperature (SST) anomaly from 1985 to 2024 over coral reefs of `r area_i`. The black line is the long-term trend in SST anomaly, values below this line are negative SST anomalies (*i.e.* cooler than long-term trend), and values above this line are positive SST anomalies (*i.e.* warmer than long-term trend).

\

```{r echo=FALSE, message=FALSE}

sst_lt <- read_xlsx("../../figs/01_part-1/tbl-3.xlsx") %>% 
  filter(area == area_i) %>% 
  select(mean_sst) %>% 
  pull()

sst_trend <- read_xlsx("../../figs/01_part-1/tbl-3.xlsx") %>% 
  filter(area == area_i) %>% 
  select(sst_increase) %>% 
  pull()

sst_rate <- read_xlsx("../../figs/01_part-1/tbl-3.xlsx") %>% 
  filter(area == area_i) %>% 
  select(warming_rate) %>% 
  pull()

```

The long-term average in SST from 1985 to 2024 over coral reefs of `r area_i` was `r sst_lt` °C. Over this period, SST increased by `r sst_trend` °C, representing a warming rate of `r sst_rate` °C per year

\

\newpage

### 2.2 Hurricanes

\

```{r echo=FALSE, message=FALSE}

data_cyclones_i <- data_cyclones %>% 
  filter(area == area_i)

nb_storm <- length(unique(data_cyclones_i$ts_id))

data_cyclones_i <- data_cyclones_i %>% 
  filter(area == area_i) %>% 
  filter(windspeed >= 100)

nb_cyclone <- length(unique(data_cyclones_i$ts_id))

data_cyclones_i <- data_cyclones_i %>% 
  filter(area == area_i) %>% 
  filter(windspeed == max(windspeed))

name_cyclone <- str_to_title(data_cyclones_i$ts_name)

year_cyclone <- year(data_cyclones_i$time)

dist_cyclone <- round(data_cyclones_i$dist)

speed_cyclone <- round(data_cyclones_i$windspeed)

```

Between 1980 and 2024, a total of `r nb_storm` tropical storms passed within 100 km distance from a coral reef of `r area_i`, and of these `r nb_cyclone` were characterized by sustained wind speed greater than 100 km.h^-1^ (**Figure 2.`r nb_chapter`.3**). The cyclone with the highest sustained wind speed over the studied period was the cyclone `r name_cyclone`, in `r year_cyclone`, which passed `r dist_cyclone` km from a coral reef with sustained wind speed of `r speed_cyclone` km.h^-1^.

\

```{r echo=FALSE, message=FALSE}

figure_path <- paste0("../../figs/02_part-2/fig-3/", territory_name, ".png")

```

![](`r figure_path`)

**Figure 2.`r nb_chapter`.3.** Maximum sustained wind speed of tropical storms passing within 100 km of a coral reef between 1980 and 2024 in `r area_i`. Colors correspond to the cyclone’s Saffir-Simpson category along its entire track. However, the values of sustained wind speed are extracted from the nearest tropical storm position from a coral reef. For this reason, some sustained wind speed values are below the lower threshold of category 1 Saffir-Simpson scale (*i.e.* 119 km.h^-1^). Note that cyclones passing more than 100 km away from coral reefs of `r area_i` are not represented, although they can have had an impact.

\newpage

### 2.3 Other threats

\

\newpage

## 3. Trends in benthic cover

\

**Table 2.`r nb_chapter`.2.** Summary of monitoring data used to model temporal trends of major benthic categories.

```{r echo=FALSE, message=FALSE}

read_xlsx("../../figs/01_part-1/tbl-4.xlsx") %>% 
  filter(area == area_i) %>% 
  select(nb_sites, nb_surveys, nb_datasets, first_year, last_year) %>% 
  t() %>% 
  as.data.frame() %>% 
  bind_cols(V2 =  c("Number of sites", "Number of surveys", "Number of datasets",
                    "First year with data", "Last year with data"), .) %>% 
  flextable() %>% 
  delete_part(part = "header") %>% 
  theme_box() %>% 
  set_table_properties(., width = 0.95, layout = "autofit")

```

\

```{r echo=FALSE, message=FALSE}

figure_path <- paste0("../../figs/02_part-2/fig-4/", territory_name, ".png")

```

![](`r figure_path`)

**Figure 2.`r nb_chapter`.4.** Temporal distribution of surveys from datasets included in the analyses to model temporal trends of major benthic categories.

\newpage

```{r echo=FALSE, message=FALSE}

figure_path <- paste0("../../figs/02_part-2/fig-5/", territory_name, ".png")

```

![](`r figure_path`){width=85%}

**Figure 2.`r nb_chapter`.5.** Modeled temporal trends for hard coral (A), coralline algae (B), macroalgae (C), turf algae (D), and Other fauna (E) cover in coral reefs of `r area_i` from 1980 to 2024. The bold line represents the estimated average cover, lighter and darker ribbons represent 95% and 80% confidence intervals, respectively. Note the scale on the y-axes are different between the four subplots. Gray areas represent periods where no observed data were available.

\newpage

## References

\

TO BE ADDED
